---
title: "titanic"
output: html_document
---


#Data Wrangling 2 Titantic


## 0 Import the Data
```{r}
library(readr)
library(tidyr)
library(dplyr)


titanic_original <- read_csv("C:/Users/Michael/Desktop/SpringBoard/titanic_original.csv")
```


##1 Change NA to S in Embarked


```{r}
titanic_original$embarked[titanic_original$embarked == ""] <- "S"
```

Test to see if any remaining NA

```{r}
which(is.na(titanic_original$embarked))
```

## 2 Find the mean Age and Replace NA values with it

```{r}
mean_age <- mean(titanic_original$age, na.rm = TRUE)

titanic_age <- replace_na(titanic_original, replace = list(age = mean_age))
```


I would suggest using the median age potentially as the mean could be skewed to a younger or older age giving a a set of extremes on those ages. Additionally you could look to calcuate a mean based on one or two standard deviations, this may give a more accurate mean.


## 3 LifeBoat fill in NONE

```{r}
titanic_lifeboat <- titanic_age %>%
  replace_na(list(boat = "none"))
```



I could not get these following codes to work and I amnot sure why, also na would not change in cabing as well

```{r}
titanic_lifeboat <- titanic_age 
titanic_lifeboat[titanic_lifeboat$boat == ""] <- "None"

titanic_lifeboat$boat <- sub("^$", "none", titanic_lifeboat$boat)


titanic_lifeboats <- titanic_age %>%
  mutate(boat = sub("^$", "None", boat))  
```

  
##4 Add Has a Cabin colum for if they did or did not


```{r}
titanic_cabin <- titanic_lifeboat %>% mutate(has_a_cabin = ifelse(cabin == "", "0", "1") )
```

It does not make sense to fill in missing cabin numbers with a value as they are all
unique and distinct unless you could come up with a more accurate way to base where they
might be located for cabins based on other variables.

##5 Create CSV

```{r}
write.csv(titanic_cabin, "titanic_clean.csv")
```

